Multiscale Modeling of the Paradoxical Roles of the Immune System in EMT-Mediated Cancer

### 2019-01-11 Paper/Paper.tex
Fixed Fig 1 Mut Example
The mutant example on the right was shifted too far down. I fixed this.

\subsection{Exploring the Model}\label{ExplModel}
Refer to Figure \ref{fig:ModelIntro}A for a cartoon of the model.
For a typical {\it in silico} patient, see Figure \ref{fig:ModelIntro}D.
Notice that at cell cycle number 541 the proportion of mutated cells reaches 50\% and so the patient has a Time to Cancer of 541.
Also of interest, as the patient's cells are all rapidly mutating right around this time, most of them are also transitioning to a mesenchymal phenotype with all of them being in a mesenchymal phenotype for a short time during the time period that cancer onset occurs.
Finally, considering a cohort of $N=500$ patients, we can generate a survival curve for these patients tracking how many have survived cancer-free up to a give day.
See Figure \ref{fig:ModelIntro}C for such a survival curve.
In this curve, we see that all patients survive for some minimum amount of time before a time period a nearly constant cancer onset rate roughly between $T = 100$ and $T = 300$.

>>>>

\subsection{Exploring the Model}\label{ExplModel}
Refer to Figure \ref{fig:ModelIntro}A for a cartoon of the model.
Here, each cell is represented as a column with three components representing the three possible mutations a cell can have.
If the component is red and has an `X' in the middle, then that indicates the cell has undergone a pathway mutation corresponding to the example cell on the right.
If any component of a cell has a pathway mutation, that cell is then counted as a mutated cell and contributes towards the total number of cancer cells.
Each cell also has a color along the EMT spectrum seen on the left of the cell block. 
Biologically, cells can be anywhere along this continuum with research indicating there are several equilibria along the spectrum.
In our model, this is actually just a binary and that is why the cells shown are at one extreme or the other of the spectrum.
In the right half of Figure \ref{fig:ModelIntro}A one can see the cell cycle choices that each cell can make each cell cycle.
These are the four thick, gray arrows.
Each of the 
For a typical {\it in silico} patient, see Figure \ref{fig:ModelIntro}D.
Notice that at cell cycle number 541 the proportion of mutated cells reaches 50\% and so the patient has a Time to Cancer of 541.
Also of interest, as the patient's cells are all rapidly mutating right around this time, most of them are also transitioning to a mesenchymal phenotype with all of them being in a mesenchymal phenotype for a short time during the time period that cancer onset occurs.
Finally, considering a cohort of $N=500$ patients, we can generate a survival curve for these patients tracking how many have survived cancer-free up to a give day.
See Figure \ref{fig:ModelIntro}C for such a survival curve.
In this curve, we see that all patients survive for some minimum amount of time before a time period a nearly constant cancer onset rate roughly between $T = 100$ and $T = 300$.
